---
title: "STAT295 HOMEWORK-2"
author: "Ali Altuntaş, Rubar Akyıldız"
date: "2024-05-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, include=FALSE}
library(tidyverse)
library(ggplot2)
library(readr)
library(dplyr)
library(broom)
```

# HOMEWORK 2

## Question 1:

### i)

```{r q_1}
data <- read.csv("social_network_ad.csv")
head(data)
ggplot(data, aes(y=EstimatedSalary, x= as.factor(Purchased)))+ 
  geom_boxplot(color= "blue",
             size=2,
             alpha=.8) +labs(x="Purchased",
                             y="Estimated Salary",
                             title ="Estimated Salary - Purchased")
```

A brief commentary about the dataset:

#### General Structure:

**Columns**:

-   **User.ID:** This column is an integer and it is used to give each customer a unique identity.

-   **Gender:** This column is a string value to distinguish genders of given customers.

-   **Age:** This is an integer column that indicates the age of the individuals.

-   **GiftTicket:** This column is a binary variable that shows whether a gift coucher was issued or not.

-   **Purchased:** This column is a binary variable that shows whether the product was puchased or not.

-   **EstimatedSalary:** This column is an integer variable that gives the estimated salaries of each individual.

#### Characteristics:

**Data Type**:

-   The dataset includes both numerical and categorical data.

-   The `User.ID`, `Age`, `GiftTicket`, `EstimatedSalary` and `Purchased` columns are numerical.

-   The `Gender` column is categorical.

**Size and Unique Values**:

-   Assuming `User.ID` is unique for each row, it implies that the dataset has a number of rows equal to the number of unique customers.

-   `Gender` is likely to have a small number of unique values, typically two (male and female).

-   `Age` may have a wide range of values depending on the demographic spread of the dataset.

-   `EstimatedSalary` may have a wide range of values depending on the demographic spread of the dataset.

-   `GiftTicket` and `Purchased` being binary, each will have two unique values.

### ii)

```{r}
regmodel <- glm(Purchased ~ EstimatedSalary, data= data, family = binomial())
 summary(regmodel)
 
exp(regmodel$coefficients[2])
```

As the odds ratio for Estimated Salary function is slightly greater than 1, we have positive association between purchasing and probabity of purchasing.

Odds of purchasing increases by 1.00024 for each unit increase in the EstimatedSalary

```{r}
est_22k <- data.frame(EstimatedSalary = 22000)
predict(regmodel, est_22k, type="response")
```

According to our predictions, the probability of an individual with \$22.000 salary to purchase the product is 0.142.

### iv)

```{r}
data$Gender[data$Gender == "Male"] <- 1
data$Gender[data$Gender == "Female"] <- 0
data$Gender <- as.factor(data$Gender)

model_gender <- glm(Purchased ~ Gender, data = data, family = binomial(link = logit))
exp(model_gender$coefficients[2])
summary(model_gender)
```

The odds of Male individuals purchasing a product is 0.838 times more than Female individuals.

### v)

```{r}
model_gtp <- glm(Purchased ~ GiftTicket, data = data, family = binomial())
exp(model_gtp$coefficients[2])
model_gtp %>% summary()
```

Odds of purchase increases by 15.77 when GiftTicket received.

### vi)

```{r}
gift_yes <- data.frame(data$GiftTicket == 1)
#gift_yes <- data.frame(as.numeric(GiftTicket == 1))
#gift_no <- data.frame(GiftTicket == 0)
predict(model_gtp, gift_yes, type="response")
```

## Question 2:

```{r, eval=FALSE}
#Code does not work. I could not work on in properly.
libraries <- c("ggplot2","shiny", "tidyverse", "magrittr",
               "leaflet", "dplyr", "rvest", "sqldf", "httr")
lapply(libraries, require, character.only = TRUE)

ui_students <- fluidPage(
  titlePanel("Student Information Panel"),
  sidebarLayout(
    sidebarPanel(
      selectInput(inputId = "Gender", label = "Gender",
                  choices = c("male","femaleput")),
      selectInput(inputId = "Ethnicity", label = "Ethnicity",
                  choices = c("group A", "group B", "group C", "group D","group E"))
    )
  ),
  mainPanel(
    plotOutput("plot")
  )
)

server_stundents <- function(input, output){
  output$plot <- renderPlot({
    df <- read.csv("StudentsPerformance.csv")
    ggplot(df,aes(x = df$math.score) + )
  })
}

shinyApp(ui = ui_students, server = server_students)
```
